In this thesis when i refer to HTML5 i'm not speaking only about the HTML5 tag reference. I am speaking about
a set of thechnologies and specifications related to HTML5. It includes the \ac{HTML5} specification itself,
the \ac{CSS3} recomendations and a whole new set of \js{} APIs. So, first things first, lets make some
clarification:
\begin{description}
	\item[HTML5] refers to a new set of semantic tag (like \ctag{footer}, \ctag{header}, \ctag{article}, \ldots),
	media tags (like \ctag{video} or \ctag{audio}) and the so called Web Form 2.0.
	\item[CSS3] refers to the presentation layer specification including image effects, 3D transformation,
	tag selectors and form element validation.
	\item[JS] refers to the new set of API provided, that enable interaction with all these new elements, and additional,
	non tag-related, functionalities (like WebSockets or WebWorkers).
\end{description}

% TODO da vedere dove metterlo
With the advent of \ac{HTML5}, like any new web-technology, many problems were resolved and many others
have been created. The main issue with using HTML5 is the browser compatibility and browser-specific methods.
Every borowser has its own implementation of the HTML5, this is mainly due to the early implementation
of draft specification\footnote{In fact HTML5 (at the time of writing) is not yet standardized, is still
a draft. See \url{http://www.w3.org/TR/html5/}}.

To avoid browser inconsistency we could use \js{} frameworks. Frameworks like \citetitle{jquery} provide
a layer of abstraction between browser-specific code and the user, giving developers \js{} fallbacks for the most
common API and additional features not covered by the standard implementation. Other tools like \citetitle{modernizr}
give developers the ability to test if some HTML5 features are supported or not and provide a general fallback system
for dynamically loading polyfills\footnote{A polyfill is a \js{} library or third part plugin that emulates one or more HTML5
features, providing websites to have the same \emph{look and feel} also on older browser.}.

Now i will analyze in detail the main features of HTML5 to better understand their usefullness.
% TODO davvero?

% TODO Audio Tag???

\paragraph{Canvas}
	Let's start with the official definition\footnote{Got from the specs:
	\url{http://www.w3.org/TR/html5/the-canvas-element.html\#the-canvas-element}}
	\begin{quoting}\rm\tt
		The canvas element provides scripts with a resolution-dependent bitmap canvas, which can
		be used for rendering graphs, game graphics, or other visual images on the fly.
	\end{quoting}

	So basically is a \emph{Canvas}, like the name says, but give the developer the access to the raw pixel
	data of the canvas contents. Also in the canvas element you can draw the image taken from an \ctag{img}
	tag or a frame from a \ctag{video} tag. As you can se now we have the capability to manage image data
	directly and perform client-side task like image analisys or video manipulation.
	Obviously there are plenty of \js{} libraries that give you methods to perform image filtering or
	generally image manipulation (like \href{http://www.pixastic.com/}{Pixastic} or \href{http://camanjs.com/}{Camanjs}),
	other libraries give you the possibility to create images on the fly (like \href{http://raphaeljs.com/}{Raphaël}
	or \href{http://processingjs.org/}{Processingjs}).

	% TODO trovare dove metterlo e come collegarlo
	The canvas element also provide a 3D context to draw and animate\footnote{Animation is not natively supported, you
	must code it yourself.} high definition graphics and models using the WebGL API. This API is mantained by
	the \href{http://www.khronos.org/}{Khronos Group} and is based on OpenGL ES 2.0 specifications. On top of these
	API there are a lot of libraries\footnote{For a reference see \url{http://en.wikipedia.org/wiki/WebGL\#Developer_libraries}}
	created for easy development, the most used is the \href{http://mrdoob.github.com/three.js/}{Three}
	\js{} library, that ca be used for creating and animating 2D or 3D scenes in the canvas element.

\paragraph{WebSocket}
	% TODO Sembra buttato li da rivedere
	The WebSocket is an API interface for enabling bi-directional full-duplex server communication on top of the \ac{TCP} protocol.
	The WebSocket enables the clients to create a communication channel between the server and the client, allowing the server
	to \b{push} data to the clients and obtain \emph{real} real-time content updates.

	Like other HTML5 features, WebSocket has a library, build on top of the API, that provides easy access to these functionality
	as long as a couple of fallbacks. \citetitle{socket} provide a single entry-point to create a connection to the server and
	manage the message exchange, it also provide a few fallbacks\footnote{ WebSocket, Adobe\reg
	Flash\reg Socket,
	AJAX long polling, AJAX multipart streaming, Forever Iframe,JSONP Polling} to ensure cross-browser compatibility.

	% Esempio di funzionamento?

\paragraph{WebWorkers}
	A problem you have to face when you are building computationally heavy \js{} code is its single thread nature.
	Every script runs in the same thread, this can lead to some unwanted behaviour like browser freezing or the newly
	introduced warning dialog "\emph{A script is slowing the browser}". The browser shows the dialog to prevent freezing of crashing of the
	whole bowser application, but this dialog prevent the script to fullfill their task. So how can we execute long running
	\js{} computation if the browser stop the code?

	\cite{jenkin2008parasitic} proposed a timed-based programming structure that ensure the code to be run without any browser warning
	and also offer the developer to tweak the performance of the script by dynamiccaly adjusting the interval between the step execution.
	This method leaverage on the \code{setTimeout} function of javascript in order to split code into timestep-driven code chuncks to execute.
	Here is an example of loop translated into a time-based loop:
	\begin{multicols}{2}
		\begin{algorithm}[H]
			\While{condition}{
				...do something...
			}
		\end{algorithm}

		\vfill
		\columnbreak

		\begin{algorithm}[H]
			\SetKwBlock{procedure}{procedure}{}
			\SetKwFunction{setTimeout}{setTimeout}

			\procedure(STEP){
				...do something...\\
				\If{condition}{
					\setTimeout{STEP, delay}
				}
			}
		\end{algorithm}
	\end{multicols}

	Obviously this is not a solution it is a way to hack the browser \js{} performance monitor and avoid the warning dialog.
	WebWorkers provide a standard way to create \emph{Workers} that execute in background, also performing heavy computation without harming
	the browser flow. Let's provide an official definition:
	\begin{quoting}\rm\tt
		The WebWorkers specification defines an API for running scripts in the background independently of any user interface scripts.
		This allows for long-running scripts that are not interrupted by scripts that respond to clicks or other user interactions,
		and allows long tasks to be executed without yielding to keep the page responsive.
	\end{quoting}

	So basically fills the gap of parallel code execution in \js{}.