% Enabling web-based distributed computation

% iniziative per facilitare la scrittura di app  lato client emscipten/google
% web tooklit engine

% parlo del we come piattaforma condivisa per distribuzione del codice
% TODO evoluzione del web prima content delivery ora RIA
% RIA (HTML4) mancavano accesso ai dati, data storage e comunicazione
% HTML5 ->
%% Comunicazione CORS e WeBSocket
%% Accesso ai dati File API, canvas
%% dataStorage (prima server side) ora LoscalSotrage (WebSQL/indexedDB)

Using the web (i.e. the browser) as a platform for distributing and executiong
code implies that the available technologies are powerful enough to perform
high-level \emph{computation} and real-time \emph{communication}.
These are the requirements for evaluating if the web is a suitable platform for
code distribution.\\

\paragraph{Computation} is the key for being able to perform task within the
browser. \emph{Computation} can involve any kind of operation on the data, and
the data itself can be of any type. For instance creating an application that
analyze audio files is relatively simple using standard languages (e.g. C, C++,
Java, etc) and until a few years ago was almost\footnote{Without using strange
interaction between Flash/Silverlight and the browser.} impossible to do within
a browser, or creating a image manipulation program that runs without external
plugins.

HTML5 filled the gap that existed between any "standard" language and \js{}
giving the developers access to all the required APIs needed to create fully
functional web-applications. In \ref{sec:bg:web:html5} are presented all the
features, along with some technical details, that have enabled these evolution.\\

There are also initiatives that aim at simplify the deployment of \js{}
application. Since most of the developers have experience on languages other than
\js{} there is the need of creating application in one language and \emph{cross
comiling} it for the web. Projects like \citetitle{emscripten} and \citetitle{gwt}
offer the possibility to write the code directly in C,C++ (\citetitle{emscripten})
or Java (\citetitle{gwt}) and compile it into pure, and optimized, \js{}.

\citetitle{emscripten}, by Mozilla, is an LLVM-to-JavaScript compiler. It takes
LLVM bitcode (which can be generated from C/C++ using Clang, or any other
language that can be converted into LLVM bitcode) and compiles that into \js{}.
Since it is a compiler it offers miltiple grades of optimization that reduce the
size of the \js{} file and speedup the computation. The website is full of demos
of the ported application, including games, 2D/3D game engines, various libraries
and also SQLite.

\citetitle{gwt}, by Google, is a development toolkit for building and optimizing
complex browser-based applications. Its goal is to enable productive development
of high-performance web applications without the developer having to be an expert
in browser quirks, XMLHttpRequest, and \js{}.\\



\paragraph{Comminication} is being empowered, with respect to HTML4, by
introducing \emph{WebSocket}, that enable full-duplex data exchange with the server,
and also \ac{CORS} that give the developers the possibility to make \ac{AJAX}
requests to "foreign" servers (other than \code{localhost}) without the need of
a proxy for forwarding the requests.

\subsection{\acs{HTML}5}
\label{sec:bg:web:html5}
\input{Capitoli/Background/HTML5}


\subsection{WebCL}
\label{sec:bg:web:webcl}
\input{Capitoli/Background/WebCL}


% TODO mmm non mi convince
The availability of all those technical API give the possibility to create a
system capable of performing any \emph{Human} or \emph{Automatic} computation
task without the need of external plugins. We used all the features of HTML5
for the computation side of the System, WebSocket are used for real-time task
monitoring and with the \ac{CORS} are used within the task to request any
external data that a \emph{Requester} need.
