% !TEX encoding = UTF-8 Unicode
% !TEX TS-program = pdflatex
% !TEX root = ../Tesi.tex
% !TEX spellcheck = it-IT

%************************************************
%\chapter{Background}
\chapter{The Background}
\label{cap:bg}
%************************************************


In this chapter are presented the main fields in wich a \emph{\myTitle} falls,
providing a brief introduction to the term used and the core concepts that will
be used during the exposition.

In \autoref{sec:bg:crowd} will introduce the concept of \emph{distributed
computing}, focusing on \emph{\ac{HC}} and \emph{Automatic computation}, from
both the theoretical point of view and to the state of the art tools that
leverages on this techniques.

In \autoref{sec:bg:web} will present the web technologies that enables the 
use of the \emph{distributed computing} paradigm over the web, focusing on the
computational part of the \emph{distributed computing} process.

% TODO rifa
\comment{

Recent years have seen an increasing interest in \emph{Human Computation}
and \emph{Crowdsourcing} areas. One of the reason they are becoming
so attractive is the growth of the Web. This has allowed to leverage
the ability of people over the internet to perform tasks that even
modern computers cannot achieve properly.

This chapter, first, focus on the key steps and developments
in these fields that lead to the purposes of this thesis.
We provide an overview of \hyperref[sec:bg:crowd:human]{human computation} and
\hyperref[sec:bg:crowd:parasitic]{parasitic computing}, then we introduce the
technologies that enables the distributed computation on the web such as
{\hyperref[sec:bg:web:html5]{HTML5}} for the task distribution and execution
and {\hyperref[sec:bg:web:webcl]{WebCL}} for the task execution.

}

\section{Crowd-based computation distribution}
\label{sec:bg:crowd}
\input{Capitoli/Background/Crowd-based}



\section{Enabling web-based distributed computation}
\label{sec:bg:web}
\input{Capitoli/Background/Web-enabling}