%************************************************
\chapter{Conclusion and future works}
\label{cap:conclusion}
%************************************************

In this thesis we proposed a novel approach for web-based human and machine
computation. By leveraging on the features offered by modern Web browsers,
we provide a framework for designing and implementing general purpose Tasks.
This system allows the user to configure the Task at abstract level and add
all the required custom implementations later, even during the execution.
On top of that our framework offer the possibility to plugin external
logic to tweak the Task execution flow. With this pluggable behavior our framework
is able to support any application archetype (human, automatic and hybrid).
We validated our approach by implementing several use case applications, which demonstrate the framework by stressing its architectural configurations. 

\section{Future work}
The described work is the begin of a broaden research activity. For instance our 
framework can be extended to meet the scenario proposed by \cite{karame2011pay}.
The authors of this paper suggest the creation of an online marketplace where
the users can gather \emph{credits} by performing Task and then use these credits
as payment method for online contents (like newspapers, images, video, etc.).
From a technical point of view, our work can be extended as follows:
\begin{itemize}
    \item Better support for image processing with optimized libraries.
    \item Enhanced Task creation with the implementation of wizards that guide
    the user though the Task creation.
    \item Enriching of the framework with the addition of supported application
    archetype.
\end{itemize}