%************************************************
%\chapter{Use cases}
\chapter{Use-cases}
\label{cap:cases}
%************************************************

In the previous chapter we introduced a framework for web-based human and machine
computation, able to handle different types of application archetypes. In this
chapter we present the use-cases use to test this framework under different
scenarios. Since we wanted to test the framework with all the possible application
archetypes we implemented three use-cases: \emph{Automatic}, \emph{Human} and
\emph{Hybrid}:
\begin{description}
    \item[Automatic:] the automatic use-case is used to simulate a
    \emph{Distributed Computing} application. In this scenario we compute the
    SIFT algorithm on an image and return the obtained keypoints to the server.
    \item[Human:] the human use-case is used to test if we can perform \acl{HC}
    with our framework. To test this scenario we implemented a text disambiguation
    application.
    \item[Hybrid:] the hybrid use-case is used to test both the automatic and the
    human scenarios. Here we implemented a \ac{GWAP} on top of a face recognition
    algorithm.
\end{description}
\noindent We focused on the implementation of the \emph{Voluntary} scenario, see
\autoref{tab:matrix}, because the \emph{involuntary} case is almost straightforward
to obtain.
At the end of every use-case will be presented, if possible, a simple
benchmark/metric where the use-case results are compared with the ones obtained
with the available tools. 



\section{Automatic}
\label{sec:cases:automatic}
\input{Capitoli/Use-case/Automatic}

\section{Human}
\label{sec:cases:human}
\input{Capitoli/Use-case/Human}


\section{Hybrid (automatic \& human)}
\label{sec:cases:hybrid}
\input{Capitoli/Use-case/Hybrid}